### 2014-11-07 fundamentals/examples.tex
minor edits for QA and one typo in Examples
minor edits

The success of the \Cyclus simulator is illustrated by demonstrations
of its fundamental simulation capabilities and the feasibility of \Cyclus
as a community-driven development model.
%The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
%model and of fundamental simulation capability. 
Nascent promising growth of the \Cyclus 
The success of the \Cyclus simulator can be measured in many ways. 
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
model and of fundamental simulation capability. Nascent promising growth of the \Cyclus 
ecosystem at multiple institutions indicates that a fuel cycle simulator can 
advance in a community-drive development paradigm. Additionally, simple 
simulations as well as more complex recycling simulations demonstrate that 
\Cyclus possesses fundamental fuel cycle simulation capabilities.

@@

The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
archetypes, data, and input files intended for use with the \Cyclus simulator. 
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
repository
\item the archetypes created by researchers
\item isotopic composition data
\item historical facility deployment data
\item the \Cyclus \gls{GUI} tool Cyclist
\item fundamental analysis tools in the \Cyclus toolkit
\item tools for \Cyclus optimization, parallelization, and development
\end{itemize}
Taken together, these form an `ecosystem' of capabilities. Over time, this 
ecosystem will grow as archetype-developers, kernel-developers, and 
even users contribute capabilities developed for their own needs. Indeed, the 
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
of both general and specialized capability extensions within the ecosystem.

@@

Many archetypes external to the \Cycamore library (Table \table{tab:cycamore})  
have been 
\cite{huff_streamblender_2014,huff_commodconverter_2014}
or are being 
\cite{flanagan_bright-lite_2014,skutnik_nuclear_2014,huff_mktdriveninst_2014} developed for contribution to the 
\Cyclus ecosystem. These archetypes provide the first examples of 
developer-contributed capabilities.  They add to the fundamental \Cycamore
archetypes by providing physics-based reactors, separation, fabrication, and storage
facilities, and expanded institutional paradigms.  These contributed archetypes
illustrate the power of a community-based development approach.

>>>>

The success of the \Cyclus simulator is illustrated by demonstrations
of its fundamental simulation capabilities and the feasibility the
 community-driven \Cyclus development model.
Nascent promising growth of the \Cyclus 
The success of the \Cyclus simulator can be measured in many ways. 
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
model and of fundamental simulation capability. Nascent promising growth of the \Cyclus 
ecosystem at multiple institutions indicates that a fuel cycle simulator can 
advance in a community-drive development paradigm. Additionally, simple 
simulations as well as more complex recycling simulations demonstrate that 
\Cyclus possesses fundamental fuel cycle simulation capabilities.

@@

The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
archetypes, data, and input files intended for use with the \Cyclus simulator. 
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
repository
\item the archetypes created by researchers
\item isotopic composition data
\item historical facility deployment data
\item the \Cyclus \gls{GUI} tool Cyclist
\item fundamental analysis tools in the \Cyclus toolkit
\item tools for \Cyclus optimization, parallelization, and development
\end{itemize}
Taken together, these form an `ecosystem' of capabilities. Over time, this 
ecosystem will grow as archetype-developers, kernel-developers, and 
even users contribute capabilities developed for their own needs. Indeed, the 
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
of both general and specialized capability extensions.

@@

Many archetypes external to the \Cycamore library (Table \ref{tab:cycamore})  
have been 
\cite{huff_streamblender_2014,huff_commodconverter_2014}
or are being 
\cite{flanagan_bright-lite_2014,skutnik_nuclear_2014,huff_mktdriveninst_2014} developed for contribution to the 
\Cyclus ecosystem. These archetypes provide the first examples of 
developer-contributed capabilities.  They add to the fundamental \Cycamore
archetypes by providing physics-based reactors, separation, fabrication, and storage
facilities, and expanded institutional paradigms.  These contributed archetypes
illustrate the power of a community-based development approach.
